### 2017-05-10 paper/evaluation.tex
restructure

\newpage
\section{Evaluation}
\label{sec:eval}

@@

\newcommand{\numRQA}{RQ1}
\newcommand{\numRQB}{RQ2}
\newcommand{\numRQC}{RQ3}
\newcommand{\numRQE}{RQ4}
\newcommand{\numRQF}{RQ5}
\newcommand{\numRQD}{RQ6}
\newcommand{\numRQG}{RQ7}

\newcommand{\RQA}{How prevalent is the occurence of time-consuming
  test suites\Comment{ in open-source projects}?}
\newcommand{\RQB}{How time is distributed across test cases?}
\newcommand{\RQC}{How popular is test suite
  parallelization\Comment{ in open-source projects}?}
\newcommand{\RQD}{What are the speedups obtained with parallelization
  (in projects that actually use it) on cost?}
\newcommand{\RQE}{What are the main reasons that prevent developers
  from using test suite parallelization?}
\newcommand{\RQF}{How parallel execution configurations affect testing
  costs and flakiness?}
\newcommand{\RQG}{How test execution scales with the number of
  available CPUs?}

\setlist[itemize]{leftmargin=1em}
\begin{itemize}
\item Feasibility
  \begin{itemize}
  \item \textbf{\numRQA.} \RQA
  \item \textbf{\numRQB.} \RQB    
  \end{itemize}
\item Adoption
  \begin{itemize}
  \item \textbf{\numRQC.} \RQC    
  \item \textbf{\numRQE.} \RQE
  \end{itemize}
\item Tradeoffs
  \begin{itemize}
  \item \textbf{\numRQF.} \RQF    
  \end{itemize}
\item Speedups
  \begin{itemize}
  \item \textbf{\numRQD.} \RQD
  \item \textbf{\numRQG.} \RQG
  \end{itemize}    
\end{itemize}

%%\newcommand{\RQB}{What is the distribution of CPU and IO bound
%%regression test suites from the sample set?}
%%
%%\newcommand{\RQC}{How uniformly distributed is the execution time
%%across test cases in costly projects?}
%%
%%\newcommand{\RQD}{How often developers use the parallelism features
%%from build systems to improve runtime performance?}

\subsection{Subjects}
\label{sec:subjects}

We used \github{}'s search API~\cite{githubsearch} to identify
projects that satisfy the following criteria: (1) the primary language
is Java\footnote{In case of projects in multiple languages, the
  \github{} API considers the predominant language as the primary
  language.}, (2) the project has at least 100 stars, (3) the latest
update was on or after January 1st, 2016, and (4) the \emph{readme}
file contains the string \emph{mvn}.  We focused on Java for its
popularity.  Although there is no clearcut limit on the number of
\github{} stars~\cite{github-stars} to define relevant projects, we
observed that 100 was enough to eliminate trivial subjects. The third
criteria serves to skip projects without recent activity. The fourth
criteria is an approximation to find Maven projects.\Comment{ The
  rationale is that if the string \emph{mvn} exists in the
  \emph{readme} file, it may represent a Maven call (\eg, to compile
  or to test the project).} We focused on Maven for its popularity on
Java projects.  Important to highlight that, as of now, the
\github{}'s search API can only reflect contents from README file (not
other code elements); it does not provide a feature to search for
projects containing certain files in the dir structure (\eg{},
\emph{pom.xml}).  Figure~\ref{fig:subject-query} illustrates the query
to the \github{} API as an HTTP request.  After obtaining a list of
potential projects, we filtered those containing a \pomf{} file in the
root directory.  A Maven project may contain several sub-modules with
multiple \pomf{} files.  We based our methodology to select
experimental subjects on other recent studies in testing and
debugging~\cite{gligoric-etal-issta2015,perez-etal-icst2017}.

As of March 25th 2017, our search criteria returned \SubjectsGithub{}
subjects. Figure~\ref{fig:subjects} summarizes our sample set. From
\SubjectsGithub{} downloaded projects, \SubjectsGithubNotMaven{}
projects were not Maven or did not have a \pomf{} in the root
directory, \SubjectsGithubNotTestable{} projects were untestable
(because of missing dependencies or incompatible testing environment,
for example), and \SubjectsGithubFlaky{} projects were ``flaky''.
\Jbc{Check if this is ok $\rightarrow$} We executed each project's
test suite for three times to identify projects containing flaky tests
and ignored these tests (\ie, using the \CodeIn{@Ignore} annotation
from JUnit) to avoid introducing noise in our experiments.  Our final
set of subjects consists of \numSubjs{} projects.

@@

\begin{itemize}
    \item \numRQA{}. \textbf{\RQA}
\end{itemize}
%\Jbc{The following steps may change $\rightarrow$}

@@

\vspace{1ex}
\begin{center}
\fbox{
\begin{minipage}{8cm}
    \textit{Answering \numRQA{}:}~\emph{We conclude that
      time-consuming test suites are relatively frequent in
      open-source projects.  We found that \percentMedLongRunning{} of
      the \numSubjs{} projects we analyzed (\ie{}, over 1 in every 5
      projects) take at least 3 minutes to run and
      \percentLongRunning{} take at least 5 minutes to run.\Comment{
        (\ie, \numMedLong{} projects from \medg{} and \longg{}).}}
\end{minipage}
}
\end{center}
\vspace{1ex}

\begin{itemize}
    \item \numRQB. \textbf{\RQB}
\end{itemize}

Section~\ref{sec:rqA} showed that medium and long-running projects are
not uncommon, accounting to nearly \percentMedLongRunning{} of the
\numSubjs{} projects we analyzed.  Research question \numRQB{}
measures the distribution of test costs in test suites as to estimate
(lack of) potential of obtaining speedups with parallelization.  In
the limit, if cost is dominated by a single test from a large test
suite, it is unlikely that parallelization will be beneficial as a
test method is the smallest working unit in test frameworks.

@@

\vspace{1ex}
\begin{center}
\fbox{
\begin{minipage}{8cm}
    \textit{Answering \numRQB{}:}~\emph{Overall, results indicate that
    projects with a very small number of tests monopolizing end-to-end
    execution time were rare.}
\end{minipage}
}
\end{center}
\vspace{1ex}

@@

%% We also evaluated the dispersion of time distributions (one
%% distribution per project) to answer research question \numRQB{}.  To
%% measure dispersion \emph{across} projects we used Relative Standard
%% Deviation (RSD)~\cite{everitt-book-stats-2010}.  Note that, if we were
%% to analyze each project in isolation, the standard deviation of a
%% distribution ($\sigma$) would suffice to quantify how dispersed the
%% (time) distribution is.  However, in our case, we would like to be
%% able to compare and summarize dispersion across projects.  The RSD,
%% which is obtained dividing the standard deviation by the mean ($\mu$)
%% of a distribution, provides such normalization effect.  This metric
%% provides a lower bound (zero) but not an upper bound (somewhere close
%% to 1).  The smaller (larger) the value of RSD the more (less) uniform
%% the distribution is.  Consequently, the lower the value of RSD the
%% more parallelizable a test suite should be.

@@

The dimension adoption focuses on the usage of parallelism in
open-source projects.  It evaluates (\numRQC) how often open-source
projects use parallelization schemes and (\numRQE) how developers
involved in costly projects, not using parallelization, perceive this
technology.

\begin{itemize}
    \item \numRQC. \textbf{\RQC{}}
\end{itemize}

To answer \numRQC{}, we selected all projects from the \medg{} and
\longg{} groups, \ie, projects that ran in at least one minute.  This
set includes \numMedLong{} projects (see Section~\ref{sec:rqA}).  We
looked for dynamic and static manifestations of parallelism.

@@

\vspace{1ex}
\begin{center}
\fbox{
  \begin{minipage}{8cm}
      \textit{Answering \numRQC{}:}~\emph{Results indicate that test
        suite parallelization is underused.  Overall, only
        \percentParallel{} of costly projects (11 out of \numMedLong)
        use parallelism.}
  \end{minipage}
}
\end{center}
\vspace{1ex}

@@

\begin{itemize}
	\item \numRQE{}. \textbf{\RQE{}}
\end{itemize}

@@

Considering question 2, the answers we collected indicated, to our
surprise, that six of the \emailsProjectsAnswered{} projects execute
tests in parallel.  This mismatch is justified by cases where neither
of our checks (static or dynamic) could detect presence of
parallelism.  A closer look at these projects revealed that one of
them contained a \emph{pom.xml} file encapsulated in a jar file
(similar case as reported in Section~\ref{sec:rqC-2}), in one of the
projects the particpant considered that distributed CI was a form of
parallelism, and in four projects the team preferred to implement
parallelization instead of using existing features from the testing
framework and the build system~---~in two projects the team
implemented concurrency control with custom JUnit test runners and in
two other projects the team implemented concurrency within test
methods.  Note that, considering these four extra cases (ignored two
distributed CI cases), the usage of parallelization increases from
\percentParallel{} to \percentParallelUpdated{}.  We do not consider
this change significant enough to modify our conclusion about
practical adoption of parallelization (\numRQC{}).

@@

\begin{center}
\fbox{
	\begin{minipage}{8cm}
	  \textit{Answering \numRQE{}:}~\emph{Results suggest that dealing
       with concurrency issues (\ie{}, the extra work to organize test
       suite to safely explore concurrency) was the principal reason
       for developers not investing in parallelism.  Other reasons
       included availability of continuous integration services and
       unfamiliarity with the technology.}
	\end{minipage}
}
\end{center}

\subsection{Tradeoffs}
\label{sec:rq6-tradeoffs}

@@

\begin{itemize}
    \item \numRQF{}. \textbf{\RQF{}}
\end{itemize}

@@

\begin{center}
\fbox{
\begin{minipage}{8cm}
\textit{Answering \numRQF{}:~\emph{\Jbc{summarize findings...}}}
\end{minipage}
}
\end{center}

\begin{itemize}
    \item \numRQD{}. \textbf{\RQD}
\end{itemize}

To answer \numRQD{}, we considered \numProjectsPar{} subjects from our
benchmark that use parallelization \emph{by default} when running
tests.  In those projects, parallelization is active without passing
any extra parameters.  Section~\ref{sec:rqC-1} describes in detail the
methodology we used to find these subjects.
%and
%Section~\ref{seq:rq6-tradeoffs}, we verified that both
%% executions produce the same outcome to eliminate noise from failing
%% tests.  To compute the speedup, we divide the time obtained in the
%% sequential execution by the time obtained from the default execution.
%% For instance, if a project runs the tests sequentially in $10m$ and
%% the same execution runs in $5m$ with parallelization enabled (default
%% execution), the speedup is two.

\begin{center}
\fbox{
  \begin{minipage}{8cm}
    \textit{Answering \numRQD{}:}~\emph{ The average speedup observed
      with default configurations of parallelization was
      \avgSpeedup{}x.}
  \end{minipage}
}
\end{center}

>>>>

\newpage
\section{Objects of Analysis}
\label{sec:subjects}

We used \github{}'s search API~\cite{githubsearch} to identify
projects that satisfy the following criteria: (1) the primary language
is Java\footnote{In case of projects in multiple languages, the
  \github{} API considers the predominant language as the primary
  language.}, (2) the project has at least 100 stars, (3) the latest
update was on or after January 1st, 2016, and (4) the \emph{readme}
file contains the string \emph{mvn}.  We focused on Java for its
popularity.  Although there is no clearcut limit on the number of
\github{} stars~\cite{github-stars} to define relevant projects, we
observed that 100 was enough to eliminate trivial subjects. The third
criteria serves to skip projects without recent activity. The fourth
criteria is an approximation to find Maven projects.\Comment{ The
  rationale is that if the string \emph{mvn} exists in the
  \emph{readme} file, it may represent a Maven call (\eg, to compile
  or to test the project).} We focused on Maven for its popularity on
Java projects.  Important to highlight that, as of now, the
\github{}'s search API can only reflect contents from README file (not
other code elements); it does not provide a feature to search for
projects containing certain files in the dir structure (\eg{},
\emph{pom.xml}).  Figure~\ref{fig:subject-query} illustrates the query
to the \github{} API as an HTTP request.

After obtaining a list of
potential projects, we filtered those containing a \pomf{} file in the
root directory.  A Maven project may contain several sub-modules with
multiple \pomf{} files.\Comment{  We based our methodology to select
experimental subjects on other recent studies in testing and
debugging~\cite{gligoric-etal-issta2015,perez-etal-icst2017}.}
As of March 25th 2017, our search criteria returned \SubjectsGithub{}
subjects. Figure~\ref{fig:subjects} summarizes our sample set.

From \SubjectsGithub{} downloaded projects, \SubjectsGithubNotMaven{}
projects were not Maven or did not have a \pomf{} in the root
directory, \SubjectsGithubNotTestable{} projects were untestable
because of missing dependencies or incompatible testing environment,
for example, and \SubjectsGithubFlaky{} projects were ``flaky''.
\Jbc{Check if this is ok $\rightarrow$} We executed each project's
test suite for three times to identify projects containing flaky tests
and ignored these tests (\ie, using the \CodeIn{@Ignore} annotation
from JUnit) to avoid introducing noise in our experiments.  Our final
set of subjects consists of \numSubjs{} projects.

\section{Evaluation}
\label{sec:eval}

@@

%% Feasibility
\newcommand{\numRQFeasibilityOne}{RQ1}
\newcommand{\RQFeasibilityOne}{How prevalent is the occurence of time-consuming
  test suites\Comment{ in open-source projects}?}

\newcommand{\numRQFeasibilityTwo}{RQ2}
\newcommand{\RQFeasibilityTwo}{How time is distributed across test cases?}

%% Adoption
\newcommand{\numRQAdoptionOne}{RQ3}
\newcommand{\RQAdoptionOne}{How popular is test suite
  parallelization\Comment{ in open-source projects}?}

\newcommand{\numRQAdoptionTwo}{RQ4}
\newcommand{\RQAdoptionTwo}{What are the main reasons that prevent developers
  from using test suite parallelization?}

%% Speedups
\newcommand{\numRQSpeedupOne}{RQ5}
\newcommand{\RQSpeedupOne}{What are the speedups obtained with parallelization
  (in projects that actually use it)?}

\newcommand{\numRQSpeedupTwo}{RQ6}
\newcommand{\RQSpeedupTwo}{How test execution scales with the number of
  available CPUs?}

%% Issues
\newcommand{\numRQIssuesOne}{RQ7}
\newcommand{\RQIssuesOne}{How parallel execution configurations affect testing
  costs and flakiness?}

\setlist[itemize]{leftmargin=1em}
\begin{itemize}
\item Feasibility
  \begin{itemize}
  \item \textbf{\numRQFeasibilityOne.} \RQFeasibilityOne
  \item \textbf{\numRQFeasibilityTwo.} \RQFeasibilityTwo    
  \end{itemize}
\item Adoption
  \begin{itemize}
  \item \textbf{\numRQAdoptionOne.} \RQAdoptionOne    
  \item \textbf{\numRQAdoptionTwo.} \RQAdoptionTwo
  \end{itemize}
\item Speedups
  \begin{itemize}
  \item \textbf{\numRQSpeedupOne.} \RQSpeedupOne
  \item \textbf{\numRQSpeedupTwo.} \RQSpeedupTwo
  \end{itemize}      
\item Issues
  \begin{itemize}
  \item \textbf{\numRQIssuesOne.} \RQIssuesOne    
  \end{itemize}
\end{itemize}

%%\newcommand{\RQFeasibilityTwo}{What is the distribution of CPU and IO bound
%%regression test suites from the sample set?}
%%
%%\newcommand{\RQAdoptionOne}{How uniformly distributed is the execution time
%%across test cases in costly projects?}
%%
%%\newcommand{\RQAdoptionTwo}{How often developers use the parallelism features
%%from build systems to improve runtime performance?}

@@

\begin{itemize}
    \item \numRQFeasibilityOne{}. \textbf{\RQFeasibilityOne}
\end{itemize}
%\Jbc{The following steps may change $\rightarrow$}

@@

\vspace{1ex}
\begin{center}
\fbox{
\begin{minipage}{8cm}
    \textit{Answering \numRQFeasibilityOne{}:}~\emph{We conclude that
      time-consuming test suites are relatively frequent in
      open-source projects.  We found that \percentMedLongRunning{} of
      the \numSubjs{} projects we analyzed (\ie{}, over 1 in every 5
      projects) take at least 3 minutes to run and
      \percentLongRunning{} take at least 5 minutes to run.\Comment{
        (\ie, \numMedLong{} projects from \medg{} and \longg{}).}}
\end{minipage}
}
\end{center}
\vspace{1ex}

\begin{itemize}
    \item \numRQFeasibilityTwo. \textbf{\RQFeasibilityTwo}
\end{itemize}

Section~\ref{sec:rqA} showed that medium and long-running projects are
not uncommon, accounting to nearly \percentMedLongRunning{} of the
\numSubjs{} projects we analyzed.  Research question \numRQFeasibilityTwo{}
measures the distribution of test costs in test suites as to estimate
(lack of) potential of obtaining speedups with parallelization.  In
the limit, if cost is dominated by a single test from a large test
suite, it is unlikely that parallelization will be beneficial as a
test method is the smallest working unit in test frameworks.

@@

\vspace{1ex}
\begin{center}
\fbox{
\begin{minipage}{8cm}
    \textit{Answering \numRQFeasibilityTwo{}:}~\emph{Overall, results indicate that
    projects with a very small number of tests monopolizing end-to-end
    execution time were rare.}
\end{minipage}
}
\end{center}
\vspace{1ex}

@@

%% We also evaluated the dispersion of time distributions (one
%% distribution per project) to answer research question \numRQFeasibilityTwo{}.  To
%% measure dispersion \emph{across} projects we used Relative Standard
%% Deviation (RSD)~\cite{everitt-book-stats-2010}.  Note that, if we were
%% to analyze each project in isolation, the standard deviation of a
%% distribution ($\sigma$) would suffice to quantify how dispersed the
%% (time) distribution is.  However, in our case, we would like to be
%% able to compare and summarize dispersion across projects.  The RSD,
%% which is obtained dividing the standard deviation by the mean ($\mu$)
%% of a distribution, provides such normalization effect.  This metric
%% provides a lower bound (zero) but not an upper bound (somewhere close
%% to 1).  The smaller (larger) the value of RSD the more (less) uniform
%% the distribution is.  Consequently, the lower the value of RSD the
%% more parallelizable a test suite should be.

@@

The dimension adoption focuses on the usage of parallelism in
open-source projects.  It evaluates (\numRQAdoptionOne) how often open-source
projects use parallelization schemes and (\numRQSpeedupOne) how developers
involved in costly projects, not using parallelization, perceive this
technology.

\begin{itemize}
    \item \numRQAdoptionOne. \textbf{\RQAdoptionOne{}}
\end{itemize}

To answer \numRQAdoptionOne{}, we selected all projects from the \medg{} and
\longg{} groups, \ie, projects that ran in at least one minute.  This
set includes \numMedLong{} projects (see Section~\ref{sec:rqA}).  We
looked for dynamic and static manifestations of parallelism.

@@

\vspace{1ex}
\begin{center}
\fbox{
  \begin{minipage}{8cm}
      \textit{Answering \numRQAdoptionOne{}:}~\emph{Results indicate that test
        suite parallelization is underused.  Overall, only
        \percentParallel{} of costly projects (11 out of \numMedLong)
        use parallelism.}
  \end{minipage}
}
\end{center}
\vspace{1ex}

@@

\begin{itemize}
	\item \numRQAdoptionTwo{}. \textbf{\RQAdoptionTwo{}}
\end{itemize}

@@

Considering question 2, the answers we collected indicated, to our
surprise, that six of the \emailsProjectsAnswered{} projects execute
tests in parallel.  This mismatch is justified by cases where neither
of our checks (static or dynamic) could detect presence of
parallelism.  A closer look at these projects revealed that one of
them contained a \emph{pom.xml} file encapsulated in a jar file
(similar case as reported in Section~\ref{sec:rqC-2}), in one of the
projects the particpant considered that distributed CI was a form of
parallelism, and in four projects the team preferred to implement
parallelization instead of using existing features from the testing
framework and the build system~---~in two projects the team
implemented concurrency control with custom JUnit test runners and in
two other projects the team implemented concurrency within test
methods.  Note that, considering these four extra cases (ignored two
distributed CI cases), the usage of parallelization increases from
\percentParallel{} to \percentParallelUpdated{}.  We do not consider
this change significant enough to modify our conclusion about
practical adoption of parallelization (\numRQAdoptionOne{}).

@@

\begin{center}
\fbox{
	\begin{minipage}{8cm}
	  \textit{Answering \numRQAdoptionTwo{}:}~\emph{Results suggest that dealing
       with concurrency issues (\ie{}, the extra work to organize test
       suite to safely explore concurrency) was the principal reason
       for developers not investing in parallelism.  Other reasons
       included availability of continuous integration services and
       unfamiliarity with the technology.}
	\end{minipage}
}
\end{center}

\begin{itemize}
    \item \numRQSpeedupOne{}. \textbf{\RQSpeedupOne}
\end{itemize}

To answer \numRQSpeedupOne{}, we considered \numProjectsPar{} subjects from our
benchmark that use parallelization \emph{by default} when running
tests.  In those projects, parallelization is active without passing
any extra parameters.  Section~\ref{sec:rqC-1} describes in detail the
methodology we used to find these subjects.
%and
%Section~\ref{seq:rq6-tradeoffs}, we verified that both
%% executions produce the same outcome to eliminate noise from failing
%% tests.  To compute the speedup, we divide the time obtained in the
%% sequential execution by the time obtained from the default execution.
%% For instance, if a project runs the tests sequentially in $10m$ and
%% the same execution runs in $5m$ with parallelization enabled (default
%% execution), the speedup is two.

\begin{center}
\fbox{
  \begin{minipage}{8cm}
    \textit{Answering \numRQSpeedupOne{}:}~\emph{ The average speedup observed
      with default configurations of parallelization was
      \avgSpeedup{}x.}
  \end{minipage}
}
\end{center}

\begin{itemize}
    \item \numRQSpeedupTwo{}. \textbf{\RQSpeedupTwo}
\end{itemize}

\begin{center}
\fbox{
  \begin{minipage}{8cm}
    \textit{Answering \numRQSpeedupTwo{}:}~\emph{...}
  \end{minipage}
}
\end{center}

\subsection{Issues}
\label{sec:rq6-tradeoffs}

@@

\begin{itemize}
    \item \numRQIssuesOne{}. \textbf{\RQIssuesOne{}}
\end{itemize}

@@

\begin{center}
\fbox{
\begin{minipage}{8cm}
\textit{Answering \numRQIssuesOne{}:~\emph{\Jbc{summarize findings...}}}
\end{minipage}
}
\end{center}

### 2017-05-10 paper/intro.tex
restructure

This paper reports on an empirical study we conducted to analyze the
usage and impact of low-level parallelization in speeding up testing
in open-source projects.  This is a relevant problem given the
tremendous popularity of open-source development and regression
testing research~\cite{yoo-harman-stvr2012}.  Note that
parallelization is complementary to other approaches to mitigate
testing costs such as (safe) test
selection~\cite{Rothermel:1997:SER:248233.248262} and continuous
integration~\cite{Saff:2003:RWD:951952.952340}.  The dimensions of
analysis we considered in this study are (i) potential, (iii)
adoption, and (iii) tradeoffs, (iv) speedups.

@@

The dimension \textbf{feasibility} measures the potential of
parallelization to reduce testing costs.  In the limit,
parallelization would be fruitless if all projects used short-running
test suites or if the bulk of execution cost was dominated by a single
test in the suite.  The dimension \textbf{adoption} evaluates (i) how
often existing open-source projects use parallelization schemes and
(ii) how developers involved in costly projects (not using test suite
parallelization) perceive this technology.  It is important to measure
resistance of practicioners to the technology and to understand their
reasons.  The dimension \textbf{tradeoffs} evaluates the issues and
benefits associated with\Comment{running test suites with} the use of
possible parallel configurations.  Note that the configuration choice
affects testing cost and flakiness, caused by the non-determinism
resulted from running different schedulings of test methods and
classes.  Finally, the dimension \textbf{speedups} measures the
observed impact of parallelization\Comment{~---~when used in selected
  open-source projects~---~} in running times.  We briefly summarize
each of these dimensions in the following.

@@

\vspace{1ex}\noindent\textbf{Tradeoffs.}~
\Fix{bla bla bla bla bla bla bla blabla bla bla blabla bla bla blabla
  bla bla blabla bla bla blabla bla bla blabla bla bla blabla bla bla
  blabla bla bla blabla bla bla blabla bla bla blabla bla bla blabla
  bla bla blabla bla bla blabla bla bla blabla bla bla blabla bla bla
  blabla bla bla blabla bla bla blabla bla bla blabla bla bla blabla
  bla bla blabla bla bla blabla bla bla blabla bla bla blabla bla bla
  blabla bla bla blabla bla bla blabla bla bla blabla bla bla blabla
  bla bla blabla bla bla blabla bla bla blabla bla bla blabla bla bla
  blabla bla bla blabla bla bla blabla bla bla blabla bla bla blabla
  bla bla blabla bla bla blabla bla bla blabla bla bla blabla bla bla
  blabla bla bla blabla bla bla blabla bla bla blabla bla bla blabla
  bla bla blabla bla bla blabla bla bla blabla bla bla bla}

>>>>

This paper reports on an empirical study we conducted to analyze the
usage and impact of low-level parallelization in speeding up testing
in open-source projects.  This is a relevant problem given the
tremendous popularity of open-source development and regression
testing research~\cite{yoo-harman-stvr2012}.  Note that
parallelization is complementary to other approaches to mitigate
testing costs such as (safe) test
selection~\cite{Rothermel:1997:SER:248233.248262} and continuous
integration~\cite{Saff:2003:RWD:951952.952340}.  The dimensions of
analysis we considered in this study are (i) potential, (iii)
adoption, and (iii) flakiness, (iv) speedups.

@@

The dimension \textbf{feasibility} measures the potential of
parallelization to reduce testing costs.  In the limit,
parallelization would be fruitless if all projects used short-running
test suites or if the bulk of execution cost was dominated by a single
test in the suite.  The dimension \textbf{adoption} evaluates how
often existing open-source projects use parallelization schemes and
how developers involved in costly projects (not using test suite
parallelization) perceive this technology.  It is important to measure
resistance of practicioners to the technology and to understand their
reasons.  The dimension \textbf{issues} reports the observed problems
associated with running tests in parallel.  For example, test
flakiness, which is caused by interference on shared state from
non-deterministic executions of test methods and classes.  Finally,
the dimension \textbf{speedups} evaluates the observed impact of
parallelization\Comment{~---~when used in selected open-source
  projects~---~} in running times.  We briefly summarize each of these
dimensions in the following.

@@

\vspace{1ex}\noindent\textbf{Issues.}~
\Fix{bla bla bla bla bla bla bla blabla bla bla blabla bla bla blabla
  bla bla blabla bla bla blabla bla bla blabla bla bla blabla bla bla
  blabla bla bla blabla bla bla blabla bla bla blabla bla bla blabla
  bla bla blabla bla bla blabla bla bla blabla bla bla blabla bla bla
  blabla bla bla blabla bla bla blabla bla bla blabla bla bla blabla
  bla bla blabla bla bla blabla bla bla blabla bla bla blabla bla bla
  blabla bla bla blabla bla bla blabla bla bla blabla bla bla blabla
  bla bla blabla bla bla blabla bla bla blabla bla bla blabla bla bla
  blabla bla bla blabla bla bla blabla bla bla blabla bla bla blabla
  bla bla blabla bla bla blabla bla bla blabla bla bla blabla bla bla
  blabla bla bla blabla bla bla blabla bla bla blabla bla bla blabla
  bla bla blabla bla bla blabla bla bla blabla bla bla bla}
